HETDEX Paper

### 2015-05-28 ms.tex
worked on mass section

@@

A second effect, unique to works such as this, is the difference between the LOSVD computed between dark matter halos and the galaxies that occupy them, the so-called velocity bias (\eg, \citealt{Evrard2008, White2010}). This effect is assumed to be small ($\sim5\%$) and for this work we assume there is no bias, or that the galaxies perfectly trace the velocity distribution.

\subsection{Dynamical Mass}
Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
\begin{equation}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{\sigma_{15}} \bigg{)}^{-\alpha} \Msol
\end{equation}
where $\sigma_{15} = 1082.9 \pm 4.0~\kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0/100 \sqrt{\Omega_\Lambda + (1+z)^3 \Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies. \editorial{This doesn't appear to be the formula that I am actually using to calculate the mass. I think I am using the relation from Saro2013.}

\editorial{Need to talk about how the parameters are some what up for debate, and vary from study to study. I think we should just use the params from Evrard2008 and call it a day. We can show a figure where we fit the data for the parameters, but that seems kinda silly to calibrate the data on the the data we are trying to fit.}

>>>>

\newcommand{\citeeg}[1]{(\eg, \citealt{#1})}

@@

A second effect, unique to works such as this, is the difference between the LOSVD computed between dark matter halos and the galaxies that occupy them, the so-called velocity bias \citeeg{Evrard2008, White2010}. This effect is assumed to be small ($\sim5\%$) and for this work we assume there is no bias, or that the galaxies perfectly trace the velocity distribution.

\subsection{Dynamical Mass}
Recently, the relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
\begin{equation}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{-\alpha} \Msol
\end{equation}
with $A_{1D} =$ 1040-1140 \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).

The choice $A_{1D}$ and $\alpha$ varies between studies \citeeg{Munari2013, VanderBurg2014} and should be calibrated on a individual basis. To do this, we randomly select 47494, $z<0.5$ clusters composed of 36000 $10^{13}$, 6000 $10^{14}$ and two $10^{15}~\Msol$ halos. We perform a linear fit to the $\sigma_{1D}-M_{200}$ values allowing both $A_{1D}$ and $\alpha$ to vary. We find best fitting parameters of $A_{1D} = 1117.9~\kms$ and $\alpha = 0.3297$, both of which are very near the values from \cite{Evrard2008} of $A_{1D} = 1082.9 \pm 4.0~\kms$ and $\alpha = 0.3361$. Therefore, we chose to adopt the parameters from \cite{Evrard2008} to better facilitate with other simulations \citeeg{Old2014}, and observational studies \citeeg{Brodwin2010}.
